%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[12pt,a4paper]{moderncv}

\moderncvtheme[blue]{banking}           
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'

\usepackage[utf8]{inputenc}                   
\usepackage[scale=0.75]{geometry}
\AtBeginDocument{\recomputelengths}              

\usepackage{multicol}

\def\blue{\textcolor{black!10!red!70!}}
\def\etal{\emph{et al.~}}

\renewcommand*{\namefont}{\fontsize{25}{40}\mdseries\upshape}
\renewcommand*{\titlefont}{\fontsize{15}{40}\mdseries\upshape}

  
\firstname{Jos\'e-Alberto}
\familyname{V\'azquez Glez.\\}

\title{Instituto de Ciencias F\'isicas - UNAM}               
\address{Avenida Universidad 2001,  62210 }{Cuernavaca, Morelos} 
\phone{+777 3 29 1600}              
%\fax{1223 337523}                          
%\email{jv292@cam.ac.uk}                    
\email{javazquez@icf.unam.mx}
%\mobile{+1 777 564 7877}                    
%\extrainfo{JA Vazquez} 
%\photo[74pt]{yo}                         % '64pt'
%\quote{Some quote (optional)}                
%\nopagenumbers{}                             


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

\begin{document}
\maketitle
%
%------------------------------------------------------------------------------------------------------------
\vspace{0.5cm}


%------------------------------------------------------------------------------------------------------------
\section{Current Position}
\vspace{1.em}
%------------------------------------------------------------------------------------------------------------

\cventry{2017 - }{Investigador Asociado C, de Tiempo Completo.}
{Instituto de Ciencias F\'isicas - UNAM.}{Morelos, MX}{}{}{}
\cvline{}{Member of the SDSS-III/SDSS-IV collaboration.}
\vspace{1.em}

%An${ \breve{z}}$e
%{The application of the BAO technique to large cosmological surveys has enabled the first 
%percent-level measurements of absolute distances beyond the Milky Way. In combination with 
%CMB and SN data, these measurements yield impressively tight constraints on the 
%cosmic expansion history and correspondingly stringent tests of dark energy theories. 
%Over the next year, the strength of these tests will advance significantly with the final 
%results from BOSS and the CMB polarization and improved temperature maps from Planck. 
%In the longer term, BAO measurements will gain in precision and redshift range through 
%a multitude of ongoing or planned spectroscopic surveys, including SDSS-IV eBOSS, 
%HETDEX, DESI, WEAVE, Euclid, and WFIRST.}\\

%------------------------------------------------------------------------------------------------------------
\subsection{Research Interests}
\vspace{0.5em}
%------------------------------------------------------------------------------------------------------------

\cvline{}{BAO, CMB;  Dark Energy, Dark Matter, Inflation;  Data analysis.}
 \href{https://www.fis.unam.mx/~javazquez/}{\blue{\underline{Website}}, 
		\href{https://www.linkedin.com/in/jalbertovazquez}{\blue{\underline{LinkedIn}}}, 
		\href{https://github.com/ja-vazquez}{\blue{\underline{GitHub}}} \hfill
 \underline{https://www.fis.unam.mx/~javazquez/}
	 }
	 
%------------------------------------------------------------------------------------------------------------
\vspace{1.em}
\section{Education and Work Experience}
\vspace{0.5em}
%------------------------------------------------------------------------------------------------------------


\cventry{2016 - 2017 }{Fellowship - Catedr\'atico CONACYT.}
	{Centro de Investigaci\'on y de Estudios Avanzados [CINVESTAV].}{CDMX, MX}{}{}{}
\vspace{1.em}

\cventry{2013-2016}{Post-doctoral Research Associate, Prof.~A. Slosar.}
	{Brookhaven National Lab [BNL], U.S. Department of Energy.}{NY, USA}{}{}
\cvline{}{\emph{``Cosmological Implications of BAO measurements and Lyman-$\alpha$ forest analysis".}}
\vspace{1.em}
	%The application of the BAO technique to large cosmological surveys has enabled the first 
	%percent-level measurements of absolute distances beyond the Milky Way. In combination with 
	%CMB and SN data, these measurements yield impressively tight constraints on the 
	%cosmic expansion history and correspondingly stringent tests of dark energy theories. 


\cventry{2009-2013}{Ph.D.  in Astrophysics, Prof. A. Lasenby and Prof. M. Hobson.}
	{KICC, University of Cambridge.}{Cambridge, UK}{}{}{}
\cvline{}{\emph{``Constraining alternative cosmological models with current and future observations''.}
	\href{http://www.cosmo.bnl.gov/www/jvazquez/files/Publications.html}{\blue{\underline{[Thesis]}}}}
\vspace{1.em}
	%We present advanced  Bayesian  techniques, the computation of the Bayesian evidence, 
	%nested sampling and neural network algorithms,  to  compare alternative cosmological models 
	%in the light of the currently 
	%available data and forecasts for the next generation of experiments 


\cventry{2008-2009}{MASt. of Advanced study in Mathematics, Prof. A. Challinor.}
	{DAMTP, University of Cambridge.}{Cambridge, UK}{}{}
\cvline{}{\emph{``Constraining cosmological Inflation''.} 
\hfill \href{http://www.cosmo.bnl.gov/www/jvazquez/files/Publications.html}{\blue{\underline{[Thesis]}}}}
\vspace{1.em}
	%With the use of current and future surveys, we show constraints on the Inflationary parameters 
	%that allow us to make 
	%the connection between theoretical and observational cosmology


\cventry{2005-2007}{M.Sc. in Physics, Prof. T. Matos.}
	{Physics Department, CINVESTAV.}{DF, MX}{}{}{}
\cvline{}{\emph{``Dynamical systems in Scalar Field Cosmologies''.}
\hfill \href{http://www.cosmo.bnl.gov/www/jvazquez/files/Publications.html}{\blue{\underline{[Thesis]}}}}
\vspace{1.em}
	%In this work, by using
	%the dynamical systems formalism, we study the stability of scalar fields as the 
	%main candidates of Dark Matter

\cventry{2000-2005}{B.Sc. in Physics, Prof. T. Matos.}
	{Faculty of Sciences, UAEM. }{Morelos, MX}{}{}{}
\cvline{}{\emph{``Galaxy formation with scalar-field dark matter''.}
\hfill \href{http://www.cosmo.bnl.gov/www/jvazquez/files/Publications.html}{\blue{\underline{[Thesis]}}}}
\vspace{1.em}
	%We present the general
	%picture of the Dark matter and study several candidates, in particular single scalar fields


	 
%------------------------------------------------------------------------------------------------------------
\vspace{1.em}	
\subsection{Research Internships}
\vspace{0.5em}	 
%------------------------------------------------------------------------------------------------------------

\cventry{Jun-Oct.2013}{Visiting Researcher, hosted by Prof. T. Matos.}
{Physics Department, CINVESTAV.}{ DF, MX}{}{}{}
\cvline{}{Collaboration visit to give a lecture on `General cosmology', 
and mentor three master students in their summer projects.}
\vspace{1.em}

\cventry{2007-2008}{Graduate Research Assistant, hosted by Prof. T. Matos.}
{Physics Department, CINVESTAV.}{DF, MX}{}{}{}
\cvline{}{\emph{``Cosmological models with dynamical systems''.}}
\vspace{1.em}

\cventry{Jun-Sept.2006}{Short-term research visitor, hosted by Prof. B. Brugmann.}
{Friedrich-Schiller-Universitat Jena.}{Jena, DE}{}{}{}{}
\cvline{}{\emph{``Numerical methods in Cosmology".} }
	%The aim of this visit was to learn and work with 
	%numerical techniques in order to solve basic gravitational wave equations. } 

%------------------------------------------------------------------------------------------------
\vspace{1.em}
\section{Selected Awards \& Scholarships}
\vspace{0.5em}
%------------------------------------------------------------------------------------------------


\cvline{2018}{Proyecto de Investigac\'on e Innovaci\'on Tecnol\'ogica, PAPIIT-DGAPA.}
	\vspace{0.3em}
\cvline{2018}{Proyecto de Investigaci\'on Cient\'ifica B\'asica, SEP-CONACYT.}
	\vspace{0.3em}
\cvline{2016}{Joven Investigador Catedras CONACYT.}
	\vspace{0.3em}
\cvline{2015}{Invited for a plenary talk on behalf of the BOSS collaboration to the APS meeting.}
	\vspace{0.3em}
\cvline{2014}{Invited for a plenary talk on behalf of the BOSS collaboration to the SDSS-IV meeting.}
	\vspace{0.3em}
\cvline{2013}{Member of the National System of Researchers, Level 1 (SNI 1).}
	\vspace{0.3em}
\cvline{2013}{PhD award for academic purposes, Cavendish Laboratory, Cambridge.}
	\vspace{0.3em} %($\textsterling$ 3k)}
\cvline{2012}{Tutorial award for academic purposes, St Edmund's College, Cambridge.}
	\vspace{0.3em} %($\textsterling$ 2k)}{}{}
\cvline{2012}{American Alumni award, for traveling to the US for studies. St Edmund's College, 
	Cambridge.}
	\vspace{0.3em} %($\textsterling$ 1k)}
\cvline{2008-2012}{SEP Excellence program scholarship, complementary scholarship.}
	\vspace{0.3em} %($\sim \$$15k)}{}{}
\cvline{2008-2012}{CONACyT full scholarship, for  study towards a MASt and PhD, 
	University of Cambridge.}
	\vspace{0.3em} %($\sim \textsterling$  90k)}{}{}
\cvline{2006}{Research grant for young scientists. \emph{Awarded by the German Academic 
	Exchange Service (DAAD).} }
\cvline{2005-2007 }{CONACyT full scholarship, for  study towards a Master, CINVESTAV.}
	\vspace{0.3em} %($\sim$ MX 195k)}{}{}
\cvline{2004-2005}{Undergraduate Research Assistantship (from SNI-III tutor), UAEM-CINVESTAV.}{}{}{}
 	\vspace{0.3em}
  \cvline{2004 }{Undergraduate Teaching Assistantship,  UAEM.}

%------------------------------------------------------------------------------------------------------------
\vspace{1.em}
\subsection{Press Release}
\vspace{0.5em}
%------------------------------------------------------------------------------------------------------------


\cvline{03.2018}{TV Morelos. 	\hfill \href{algo}{\blue{link}}}
 	\vspace{0.3em}
\cvline{03.2018}{Radio UAEM.	\hfill \href{algo}{\blue{link}}}
 	\vspace{0.3em}
\cvline{03.2018}{TV interview: Stephen Hawking's life. Excelsior.
	\hfill \href{http://www.excelsior.com.mx/tv/excelsior-informa/wJHaEtUuke4}{\blue{link}}}
	 \vspace{0.3em}
\cvline{07.2016}{US Department of Energy: Dark Energy Measured With Record-Breaking Map 
	of 1.2 Million Galaxies.
	\hfill \href{https://www.bnl.gov/newsroom/news.php?a=11854}{\blue{link}}}
 	\vspace{0.3em}
\cvline{07.2016}{LBNL, Berkeley Lab: Dark Energy Measured with Record-Breaking 
	Map of 1.2 Million Galaxies.
	\hfill \href{http://newscenter.lbl.gov/2016/07/14/record-breaking-map-1-2-million-galaxies/}{\blue{link}}}
 	\vspace{0.3em}
\cvline{07.2016}{Physicsworld: Dark-energy study maps 1.2 million galaxies in the early universe.
	\hfill \href{http://physicsworld.com/cws/article/news/2016/jul/15/dark-energy-study-maps-1-2-million-galaxies-in-the-early-universe}{\blue{link}.}}
 	\vspace{0.3em}	
\cvline{04.2015}{APS meeting on behalf of the BOSS Collaboration.
	\hfill \href{http://meetings.aps.org/Meeting/APR15/Session/Z2?showAbstract}{\blue{link}}}
 	\vspace{0.3em}
\cvline{06.2012}{TV short interview: Talented Mexicans abroad. (Televisa).}{}



%------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\section{Students}
\vspace{0.5em}
%------------------------------------------------------------------------------------------------------------

\subsection{PhD}
\vspace{0.5em}	
%------------------------------------------------------------------------------------------------------------

 \cvline{Luis Enrique Padilla Albores, \hfill CINVESTAV, CDMX}{}
 		{Thesis: Scalar Field Dark Matter. \hfill Graduation date: 2019} 

\vspace{1.0em}	
 \cvline{Isidro Gomez Vargas, \hfill CICATA-Legaria, CDMX}{}
 		{Thesis: Algoritmos de mineria de datos y redes neuronales. \hfill Graduation date: 2020} 
		
\vspace{1.em}	
 \cvline{Ricardo Medel Esquivel, \hfill CICATA-Legaria, CDMX}{}
 		{Thesis: Algoritmos de la ciencia de datos en cosmologia. \hfill Graduation date: 2020} 
		
		
\vspace{1.em}	
\cvline{Luis Osvaldo T\'ellez Tovar, \hfill CINVESTAV, CDMX}{}
 		{ Thesis: Charged scalar fields as Dark Matter. \hfill Graduation date: 2021 }  

%------------------------------------------------------------------------------------------------------------	
\vspace{1.0em}
\subsection{Master}
\vspace{0.5em}
%------------------------------------------------------------------------------------------------------------
 

\cvline{Jazhiel Chac\'on Lavanderos, \hfill ICF-UNAM, Morelos}{}
 		{PCF-UNAM Cuernavaca, \hfill  2019-2021}  

%------------------------------------------------------------------------------------------------------------	
\vspace{1.0em}
\subsection{Past}
\vspace{0.5em}
%------------------------------------------------------------------------------------------------------------

\cvline{Luis Osvaldo T\'ellez Tovar, \hfill CINVESTAV, CDMX}{}
 		{Master Thesis: Constricciones de modelos de materia y energ\'ia oscura escalar. \\ 
		 Graduated: August- 2018 }  

\vspace{1.0em}		
\cvline{Luis Adri\'an Escamilla Torres, \hfill CINVESTAV, CDMX}{}
 		{Master Thesis: Reconstrucci\'on de energ\'ia oscura con base en observaciones cosmol\'ogicas.\\ 
		Graduated: November- 2018}

\vspace{0.8em}		
 \cvline{Jonathan Rinc\'on Saucedo, \hfill CINVESTAV, CDMX}{}
 		{Master Thesis: Modelos para Energ\'ia Oscura con campo escalar. 
		Graduated: November- 2018 }  
		
			
\vspace{0.8em}
\subsection{Social Service}
 \cvline{Hector hudson, \hfill UAEM, Morelos}{}
 		{Programming with Python}
		
			
%\vspace{0.8em}
%\subsection{To be Incorporated this year}

%\vspace{0.8em}
%\cvline{Rocio Amairani Arroyo Gutierrez}{}
% 		{Will present pre-doctoral exam [Classical and Quantum mechanics] to enroll at the PhD program at ICF this year, 
%		under my supervision.}  
		
%\vspace{0.8em}
%\cvline{Gabriela B\'arcenas Enriquez}{}
% 		{Will present pre-doctoral exam [Classical and Quantum mechanics] to enroll at the PhD program at ICF this year, 
%		under my supervision.} 

%------------------------------------------------------------------------------------------------------------	
\vspace{1.0em}		
\subsection{Jury member}
\vspace{0.5em}	
%------------------------------------------------------------------------------------------------------------	

	
 \cvline{11.2017}{Bachelor thesis: ``Sombras de objetos compactos''}{Yair Mart\'inez Ibarra. \hfill ESFM- IPN}
 	\vspace{1.0em}	
 
\cvline{11.2017}{Bachelor thesis: ``Modelos de Materia oscura, una perspectiva numerica''} 
	{Jazhiel Chacon Lavanderos. \hfill ESFM- IPN}


 %----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.em}
 \section{Affiliations}
\vspace{0.5em}
%------------------------------------------------------------------------------------------------------------	

\cvline{2018}{Referee of Physical Review D (PRD).}
 	\vspace{0.3em}	
\cvline{2017}{Referee of Astrophysical Journal (ApJ).}
 	\vspace{0.3em}	
\cvline{2015}{Member of the APS, AAS.}
 	\vspace{0.3em}	
\cvline{2014}{Member of the Advisory Committee for CONACYT projects (RCEA), by invitation.
  \cvline{}{ \small{Referee of projects: `Installation of a high energy and astroparticle lab', asking for \$US 300k; and 
  `Physics and astrophysics of neutron stars', asking for \$US 200k.}}}
 	\vspace{0.3em}	
\cvline{2013}{Member of the SDSS-III/SDSS-IV collaboration, as part of the BOSS/eBOSS experiment.}
  	\vspace{0.3em}	
\cvline{2012}{Committee member of the Mexican Cambridge Society.}
 	\vspace{0.3em}	
\cvline{2006}{Member of the Institute advanced  of  cosmology, \url{http://www.iac.edu.mx/}}{}{}{}
 	\vspace{0.3em}	 
\cvline{2004 -- 2005}{Counselor student at Graduate Internal Council, UAEM.}{}{}{}


%----------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\section{Publications}
\vspace{0.5em}
%----------------------------------------------------------------------------------------------------------------------------------------------------

\cvline{}{For further details and citations: 
	\hfill \href{https://inspirehep.net/author/profile/J.A.Vazquez.1}{\blue {Inspirehep}}, 
	\href{https://scholar.google.com/citations?user=PCuxBOkAAAAJ&hl=en}{ \blue{Scholar}},
	\href{https://www.researchgate.net/profile/J_Vazquez3}{ \blue{Research gate}}}
	 \vspace{1.em}


\cvline{[30] - Scalar Field Dark Matter Spectator During Inflation: The Effect of Self-interaction}{Luis E. Padilla et al.}{}{}
	\cvline{}{\qquad \href{https://arxiv.org/abs/1901.00947}{ArXiv:1901.00947}, \hfill \blue{submitted to JCAP}}
 	\vspace{1.em}

\cvline{[29] - Observational constraints on conformal time symmetry, missing matter and double dark energy}
	{J Alberto Vazquez et al. }{}{}
	\cvline{}{\qquad \href{https://arxiv.org/abs/1208.2542}{ArXiv:1208.2542}, \hfill \blue{JCAP 1807 (2018) 062}}
	 \vspace{1.em}

\cvline{[28] - The Fourteenth Data Release of the Sloan Digital Sky Survey: First Spectroscopic 
	Data from the extended Baryon Oscillation Sky Survey and from the second phase of the 
	Apache Point Observatory Galactic Evolution Experiment}
	{Bela Abolfathi et al.}
	\cvline{}{\qquad \href{https://arxiv.org/abs/1707.09322}{Arxiv: 1707.09322}, 
	\hfill \blue{Astrophys.J.Suppl. 235 (2018) no.2, 42}}
	 \vspace{1.em}
 			
\cvline{[27] - Galaxy-galaxy lensing estimators and their covariance properties:}
	{Sukhdeep Singh, Rachel Mandelbaum, Uro${ \breve{s}}$ Seljak, An${ \breve{z}}$e Slosar, JAV. }
	\cvline{}{\qquad \href{https://arxiv.org/abs/1611.00752}{ArXiv:1611.00752}, 
	\hfill \blue{MNRAS, Vol 471,  4, 11 Nov 2017}}
 	\vspace{1.em}

\cvline{[26] - The clustering of galaxies in the completed SDSS-III Baryon Oscillation 
	Spectroscopic Survey: cosmological analysis of the DR12 galaxy sample}{Shadab Alam \etal}
	\cvline{}{\qquad \href{https://arxiv.org/abs/1607.03155}{ArXiv:1607.03155}, 
	\hfill \blue{MNRAS 470 (2017) no.3, 2617-2652}}
 	\vspace{1.em}

\cvline{[25] - Sloan Digital Sky Survey IV: Mapping the Milky Way, Nearby Galaxies, and the Distant Universe}
	{Michael R. Blanton \etal}
	\cvline{}{\qquad \href{https://arxiv.org/abs/1703.00052}{ArXiv:1703.00052}, 
	\hfill \blue{Astron.J. 154 (2017) 28}}
 	\vspace{1.em}

\cvline{[24] - Measurement of BAO correlations at $z=2.3$ with SDSS DR12 Lya-Forests}
	{Julian E. Bautista \etal}
	\cvline{}{\qquad \href{https://arxiv.org/abs/1702.00176}{ArXiv:1702.00176}, 
	\hfill 	\blue{A\&A 603, A12 (2017)}}
	 \vspace{1.em}
			
\cvline{[23] - The clustering of galaxies in the completed SDSS-III Baryon Oscillation Spectroscopic Survey: 
	Examining the observational evidence for dynamical dark energy}
	{Gong-Bo Zhao  \etal}
	\cvline{}{\qquad \href{https://arxiv.org/abs/1701.08165}{ArXiv:1701.08165}, 
	\hfill \blue{Nature Astronomy, 1, 627-632, (2017)}}
	 \vspace{1.em}

\cvline{[22] - Constraining the dark energy equation of state using Bayes theorem and the 
	Kullback-Leibler divergence}{S. Hee \etal}
	\cvline{}{\qquad \href{https://arxiv.org/abs/1607.00270}{ArXiv:1607.00270,} 
	\hfill \blue{MNRAS 466 (2017) no.1, 369-377}}
 	\vspace{1.em}
	
\cvline{[21] - The clustering of galaxies in the completed SDSS-III Baryon Oscillation 
	Spectroscopic Survey: combining correlated Gaussian posterior distributions} 
	{Ariel G. Sanchez \etal}
	\cvline{}{\qquad \href{https://arxiv.org/abs/1607.03146}{ArXiv:1607.03146,} 
	\hfill \blue{MNRAS 464 (2): 1493-1501}} 
 	\vspace{1.em}		

\cvline{[20] - The clustering of galaxies in the completed SDSS-III Baryon Oscillation 
	Spectroscopic Survey: 
	Baryon Acoustic Oscillations in Fourier-space}{Florian Beutler \etal}
	\cvline{}{\qquad \href{https://arxiv.org/abs/1607.03149}{ArXiv:1607.03149,}  
	\hfill \blue{MNRAS 464 (3): 3409-3430}}	
	 \vspace{1.em}
		 
\cvline{[19] - The Thirteenth Data Release of the Sloan Digital Sky Survey: 
	First Spectroscopic Data from the SDSS-IV Survey MApping Nearby Galaxies at Apache Point Observatory}
	{Franco D. Albareti \etal} 
	\cvline{}{\qquad \href{https://arxiv.org/abs/1608.02013}{ArXiv:1608.02013}, 
	\hfill \blue{Submitted to ApJS}}
	 \vspace{1.em}
			
\cvline{[18] -The clustering of galaxies in the completed SDSS-III Baryon Oscillation Spectroscopic
	Survey: double-probe measurements from BOSS 	galaxy clustering \& Planck data -- 
	towards an analysis without informative priors } {Marcos Pellejero-Ibanez \etal}
	\cvline{}{\qquad \href{https://arxiv.org/abs/1607.03152}{ArXiv:1607.03152},  
	\hfill \blue{MNRAS. 468 (2017) no.4}}
	 \vspace{1.em}

\cvline{[17] - The Clustering of Galaxies in the Completed SDSS-III Baryon Oscillation 
	Spectroscopic Survey: single-probe measurements from DR12 galaxy clustering -- 
	towards an accurate model} {Chia-Hsun Chuang \etal}
	\cvline{}{\qquad \href{https://arxiv.org/abs/1607.03151}{ArXiv:1607.03151,}  
	\hfill {\blue{MNRAS, Vol 471, 2, 21 Oct 2017}} }	
 	\vspace{1.em}

\cvline{[16] - Hybrid Natural Inflation}{Graham G. Ross, Gabriel German, JAV.} 
	\cvline{}{\qquad \href{https://arxiv.org/abs/1601.03221}{ArXiv:1601.03221,}  
	\hfill \blue{JHEP 1605 (2016) 010}}	
	 \vspace{1.em}

\cvline{[15] - Large-scale clustering of Lyman-alpha emission intensity from SDSS/BOSS}
	{ Rupert A.C. Croft \etal}
	\cvline{}{\qquad \href{http://arxiv.org/abs/1504.04088}{ArXiv:1504.04088,}  
	\hfill \blue{ MNRAS 457 (4): 3541-3572.}}
	 \vspace{1.em}		

\cvline{[14] - Cosmological Implications of baryon acoustic oscillation (BAO) measurements}
	{\'Eric Aubourg \etal}
	\cvline{}{\qquad \href{http://arxiv.org/abs/arXiv:1411.1074}{ArXiv:1411.1074,}  
	\hfill \blue{Phys. Rev. D92 (2015) no.12, 123516}}	
	 \vspace{1.em}

\cvline{[13] - Broadband distortion modeling in Lyman-$\alpha$ forest BAO fitting}
	{Michael Blomqvist \etal} 
	\cvline{}{\qquad \href{http://arxiv.org/abs/1504.06656}{ArXiv:1504.06656,} 
	\hfill \blue{JCAP 1511 (2015) no.11, 034}}
	 \vspace{1.em}	

\cvline{[12] - The Eleventh and Twelfth Data Releases of the Sloan Digital Sky Survey:  
	Final Data from SDSS-III}{Shadab Alam \etal} 
	\cvline{}{\href{https://arxiv.org/abs/1501.00963}{ArXiv:1501.00963,} 
	\hfill \blue{ApJs 219 (2015) 1, 12}}
	 \vspace{1.em}

\cvline{[11] -  A divergence-free parametrization for dynamical dark energy}{
	Ozgur Akarsu, Tekin Dereli, JAV.}  
	\cvline{}{\qquad \href{http://arxiv.org/abs/1501.07598}{ArXiv:1501.07598,} 
	\hfill \blue{JCAP, 1506 (2015) 06, 049} }
	 \vspace{1.em}	

\cvline{[10] - Constraining Hybrid Natural Inflation with recent CMB data}
	{JAV, Mariana Carrillo, Gabriel German, Alfredo Herrera, J.C. Hidalgo.}
	\cvline{}{\href{http://arxiv.org/abs/arXiv:1411.6616}{ArXiv:1411.6616,} 
	\hfill \blue{JCAP 1502 (2015) 02, 039}}
	 \vspace{1.em}		

\cvline{[9] - Constraints on the Tensor-to-Scalar ratio for non-power law models}
	 {JAV, M. Bridges, Yin-Zhe Ma, M.P. Hobson.}
	\cvline{}{\href{http://arxiv.org/abs/1303.4014}{ArXiv:1303.4014,} 
	\hfill \blue{ JCAP~08(001)~2013}} 
	 \vspace{1.em}	

\cvline{[8] - Reconstruction of the Dark Energy equation of  state}
	 {JAV, M.P. Hobson, M. Bridges, A.N. Lasenby.}
	\cvline{}{\href{http://arxiv.org/abs/1205.0847}{ArXiv:1205.0847,}  
	\hfill \blue{JCAP, 09(020), 2012}}
	 \vspace{1.em}

\cvline{[7] - Reciprocity invariance of the Friedmann equation, missing matter and double 
	dark energy}{JAV \etal} 
	\cvline{}{\href{http://arxiv.org/abs/1208.2542}{ArXiv:1208.2542,}  
	\hfill \blue{Submitted to PRD}} 
	 \vspace{1.em}	

\cvline{[6] - Model selection applied to reconstruction of the Primordial Power Spectrum}
	{JAV, M.P. Hobson, M. Bridges, A.N. Lasenby.}
	\cvline{}{\href{http://arxiv.org/abs/1203.1252}{ArXiv:1203.1252,} 
	\hfill \blue{JCAP 006(106), 2012}}
	 \vspace{1.em}

\cvline{[5] - A Bayesian study of the primordial power spectrum from a novel closed universe}
	{JAV, A.N. Lasenby, M.P. Hobson, M. Bridges.}
	\cvline{}{\href{http://arxiv.org/abs/1103.4619}{ArXiv:1103.4619,} 
	\hfill \blue{MNRAS 422, 1948-1956, 2011}}
	 \vspace{1.em}

\cvline{[4] - Dynamics of scalar field dark matter with a cosh potential}
	{Tonatiuh Matos, Jos\'e-Rub\'en Lu\'evano, Israel Quiros, L. Arturo Urena-L\'opez,  JAV.}
	\cvline{}{\href{http://arxiv.org/abs/0906.0396}{ArXiv:0906.0396,} 
	\hfill \blue{PRD 80, 123521, 2009}}
	 \vspace{1.em}

\cvline{[3] - Self-interacting Scalar Field Trapped in a Randall-Sundrum Braneworld}
	{Tam\'e Gonz\'alez, Tonatiuh Matos, Israel Quiros, JAV.}
	\cvline{}{\href{http://arxiv.org/abs/0812.1734}{ArXiv:0812.1734,} 
	\hfill \blue{PLB 676, 161-167, 2009}} 
	 \vspace{1.em}

\cvline{[2] - $\phi^2$ as Dark Matter}{\\ Tonatiuh Matos, JAV, Juan Magana.}
	\cvline{}{ \href{http://arxiv.org/abs/0806.0683}{ArXiv:0806.0683,} 
	\hfill \blue{MNRAS 393, 1359-1369, 2008}}
	 \vspace{1.em}

\cvline{[1] - An alternative Interpretation for the Moduli Fields of the Cosmology Associated to 
	Type IIB Supergravity with Fluxes}
	{Tonatiuh Matos, Jos\'e-Rub\'en Luevano, Hugo Garc\'ia Compe\'an, JAV.} 
	\cvline{}{\href{http://arxiv.org/abs/hep-th/0511098}{ArXiv:0511098,}  
	\hfill \blue{ IJMPA  23, 1949-1962, 2008}}

%----------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.em}
\subsection{Conference Proceedings}
\vspace{0.5em}	
%----------------------------------------------------------------------------------------------------------------------------------------------------

\cvline{[4C]\quad Cosmolog\'ia Observacional y Estad\'istica}
	{\\ \qquad Jose Vazquez and Luis E. Padilla. %Cites: 2, 
	\hfill  \href{https://github.com/ja-vazquez/Cosmologia_observacional} {\blue{Verano, UNAM}}}
	\vspace{1.0em}

\cvline{[3C]\quad Cosmological Implications of baryon acoustic oscillation (BAO) measurements}
	{\\ \qquad Jose Vazquez. %Cites: 2, 
	\hfill \href{http://meetings.aps.org/Meeting/APR15/Session/Z2.5} {\blue{APS 6 No 4 (2015)}}}
	\vspace{1.0em}

\cvline{[2C]\quad Study of Several Potentials as Scalar Field Dark Matter Candidates}
	{\\ Tonatiuh Matos, JAV, Juan Magana. %Cites: 0,
	\hfill AIP Conf. Proc. 1083, 144-170, 2008. \href{http://inspirehep.net/record/808386} { \blue{AIP, 808386}}}
	\vspace{1.0em}

\cvline{[1C]\quad Alternative interpretation for the moduli fields of string theories}
	{Tonatiuh Matos, Jos\'e Rub\'en Luevano, L. Arturo Urena, JAV. %Cites:0,  
	\hfill J. Phys. Conf. Ser. 91, 012014, 2007. \href{http://inspirehep.net/record/773227} {\blue{JP, 773227}}}

%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\subsection{Reviews}
\vspace{0.5em}
%----------------------------------------------------------------------------------------------------------------------------------------------------------


\cvline{[4R] Astrobiolog\'ia: origen de la vida en el Planeta Tierra}{
	Alejandro Prieto de los Monteros1, J. Alberto V\'azquez. %Cites:~0.
	\hfill \blue{El Faro - UNAM}}
	\vspace{1.0em}

\cvline{[3R] An introduction on bayesian parameter inference and its applications in cosmology}{
	Luis E. Padilla, Alberto Vazquez and Luis O. Tellez. %Cites:~0.
	\hfill \href{https://github.com/ja-vazquez/Cosmologia_observacional/tree/master/Cosmo_stats} {\blue{RMF}}}
	\vspace{1.0em}

\cvline{[1R] Inflationary Cosmology: From Theory to Observations}{JAV, Tonatiuh Matos. %Cites:~0.
	 \hfill \href{https://arxiv.org/abs/1810.09934}{ \blue{Submitted to Rev. Mex. Fis. E.}}}
	\vspace{1.0em}
 
\cvline{[2R] Dark matter in the Universe: goals and challenges}{JAV, Tonatiuh Matos.
	Rev. Mex. de F\'isica E. 54, 193-202, 2008. %Cites:~0.
	\hfill \href{http://www.scielo.org.mx/scielo.php?pid=S1870-35422008000200012&script=sci_abstract}
	 {\blue{RMF, 1870-3542}}}

	


%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{0.5em}

\subsection{To be submitted [< 1 month] \href{http://www.cosmo.bnl.gov/www/jvazquez/files/Research.html}{\small{\blue{(link)}}}}

\vspace{0.5em}	
	
	
\vspace{0.5em}
\cvline{[5p] Decoding Horndeski theories with cosmological observations}{\\ JAV, Francisco Franco, Gustavo Niz.
	\href{http://www.cosmo.bnl.gov/www/jvazquez/files/Research.html}{\hfill \blue{Link}}}

	
\vspace{0.5em}		
\cvline{[4p] Cosmological constraints on Modified Gravity}{\\ JAV, M.P. Hobson, A.N. Lasenby, M. Bridges.
	\href{http://www.cosmo.bnl.gov/www/jvazquez/files/Research.html}{\hfill \blue{Link}}}
		
\vspace{0.5em}	
\cvline{[3p] Early Dark Energy: Reality and Fiction}{
	\\ JAV, An${ \breve{z}}$e Slosar, Hee-Jong Seo, David Weinberg.  
	\href{https://github.com/ja-vazquez/Early_DE}{\hfill \blue{Link}}} 

\vspace{0.5em}	
\cvline{[2p] Gaussian Embedding -- massively parallelizable sampling algorithm.}
	{\\ JAV, An${ \breve{z}}$e Slosar, Andreu Font-Ribera, Patrick McDonald. 
	\href{https://github.com/ja-vazquez/GM_Sampler}{\hfill \blue{Link}}}


\vspace{0.5em}	
\cvline{[1p] Fourier-law for deceleration parameter.}{\\ Ozgur Akarsu, Tekin Dereli, Suresh Kumar, JAV.  
	\href{http://www.cosmo.bnl.gov/www/jvazquez/files/Research.html}{\hfill \blue{Link}}}




%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\section{Events Organized}
\vspace{0.5em}
%----------------------------------------------------------------------------------------------------------------------------------------------------------

\cvline{08.2018}{Tonafest. \hfill cinves-UNAM, MX}{}{}{} 
	\vspace{0.3em}	
\cvline{08.2018}{Dark Matter workshop \hfill Cancun, MX}{}{}{} 
	\vspace{0.3em}	
%\cvline{10.2019}{Congreso Nacional de F\'isica. \hfill Cuernavaca, MX}{}{}{} 
\cvline{08.2018}{Gravitation and Cosmology. \hfill ICF-UNAM, MX}{}{}{} 
	\vspace{0.3em}
\cvline{07.2018}{Workshop, Numerical and Statistical methods in Cosmology. \hfill ICF-UNAM, MX}{}{}{} 
	\vspace{0.3em}
\cvline{11.2017}{CinvesPy Workshop. \hfill CINVESTAV-IPN, MX}{}{}{} 
	\vspace{0.3em}
\cvline{07.2017}{Advanced Summer School. \hfill CINVESTAV-IPN, MX}{}{}{} 
	\vspace{0.3em}
\cvline{06.2017}{XXV Reunion de la Division de Gravitacion y Fisica Matematica.  \hfill CINVESTAV-IPN, MX}{}{}{}
	\vspace{0.3em} 
\cvline{03.2017}{Workshop Organiser: Statistical and Numerical methods  in Cosmology. \hfill CINVESTAV, MX}{}{}{}  
	\vspace{0.3em}
\cvline{09.2013}{Workshop Organiser: Statistical and Numerical methods  in Cosmology. \hfill IF, UNAM, MX}{}{}{} 
	\vspace{0.3em}
\cvline{01.2011}{Mini-workshop Organiser: overview to CAMB and CosmoMC. \hfill  ININ, MX}{}{}{}


%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
 \section{Organization }
\vspace{0.5em}
%----------------------------------------------------------------------------------------------------------------------------------------------------------

\cvline{2018-}{Comisi\'on de Equidad de G\'enero del Instituto. \hfill ICF-UNAM, MX}{}{}{}
	\vspace{0.3em}
\cvline{2018-}{Seminar Organiser, ``Gravitation and Cosmology''. \hfill ICF-UNAM, MX}{}{}{} 
	\vspace{0.3em}
\cvline{2007-2008}{Seminar Organiser, ``Geometry and Gravitation''. \hfill CINVESTAV, MX}{}{}{}
	\vspace{0.3em}
\cvline{2005-2007}{Seminar  Organiser, ``Cosmology, Astrophysics and Numerical R''. \hfill CINVESTAV, MX}{}{}{}
	\vspace{0.3em}	
\cvline{2004-2005}{Committee Member, ``Consejo T\'ecnico''. \hfill UAEM, MX}{}{}{}
	\vspace{0.3em}
\cvline{2004-2005}{Committee Member, ``Consejo Estudiantil de la Sociedad de Alumnos''. \hfill UAEM, MX}{}{}{}
	\vspace{0.3em}
\cvline{2001-2002}{Committee Member, ``Consejo Estudiantil de la Sociedad de Alumnos''. \hfill UAEM, MX}{}{}{}

%------------------------------------------------------------------------------------------------------------3
\vspace{1.0em}
\section{Teaching and Outreach}
\vspace{0.5em}
%------------------------------------------------------------------------------------------------------------3

 \cvline{06.2018}{Escuela de Pertubaciones, three day course					 \hfill IF-UNAM}
 	\vspace{0.3em}
 \cvline{01.2018}{Cosmology, postgraduate course					 \hfill IF-UNAM}
 	\vspace{0.3em}
 \cvline{01.2018}{Introduction to the Modern Cosmology, undergraduate course \hfill  ICF-UNAM}
 	\vspace{0.3em}
 \cvline{08.2017}{Modern Cosmology, postgraduate course \hfill CINVESTAV}
 	\vspace{0.3em}
 \cvline{06.2017}{Mathematical Methods, Master program \hfill CINVESTAV}
 	\vspace{0.3em}
 \cvline{08.2016}{Mentoring  a summer high school student \hfill BNL}
 	\vspace{0.3em}
 \cvline{10.2015}{Mentoring  a summer high school student \hfill  BNL}
 	\vspace{0.3em}
 \cvline{07.2013}{Tutor of three Master summer students \hfill  CINVESTAV}
 	\vspace{0.3em}
 \cvline{2006 }{Graduate Research Assistant, \emph{Photo Acoustic Spectroscopy} \hfill CINVESTAV}
 	\vspace{0.3em}
 \cvline{2004-2005}{Undergraduate Research Assistantship,\emph{Galaxy Formation with dark matter} \hfill UAEM}{}{}{}
 	\vspace{0.3em}
 \cvline{2004 }{Undergraduate Teaching Assistant, \emph{Mechanics Subject} \hfill UAEM}
 	\vspace{0.3em}
 \cvline{2003-2004}{Undergraduate Research Assistantship,\emph{\small Opto-galvatinic spectroscopy of plasmas to low temperature} \hfill  {\small UAEM}} 	
 %\cvline{2001 {\tiny *}}{Undergraduate Teaching Assistant, \emph{Calculus Subject}, High School.}{\hspace{2cm}* \small Six month period.}{}	
-

%-----------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\section{Invited Talks}
\vspace{0.5em}
%-----------------------------------------------------------------------------------------------------------


\cvline{07.2018}{{tonafest.}								\hfill cinves, MX}
	\vspace{0.3em}
\cvline{07.2018}{{Platica.}								\hfill Conalep, MX}
	\vspace{0.3em}
\cvline{07.2018}{{Platica.}								\hfill Pachuca, MX}
	\vspace{0.3em}
\cvline{07.2018}{{Cosmo stats with Dark Energy.}								\hfill INAOE, MX}
	\vspace{0.3em}
\cvline{06.2018}{{Buscando Materia y Energia oscura en el Universo.}				\hfill ICF-UNAM, MX}
	\vspace{0.3em}
\cvline{05.2018}{{Energ\'ia Oscura y otros ingredientes oscuros.}					\hfill Zacatecas, MX}
	\vspace{0.3em}
\cvline{03.2018}{{Cocinando el Universo.}										\hfill ICF-UNAM, MX}
	\vspace{0.3em}
\cvline{02.2018}{{Buscando Energ\'ia Oscura con Grandes Telescopios.}				\hfill Aguascalientes, MX}
	\vspace{0.3em}
\cvline{02.2018}{{Dynamical Dark Energy from Observations.}						\hfill ICN-UNAM, MX}
	\vspace{0.3em}
\cvline{01.2018}{{Reconstruction of the Dynamical Dark Energy.}					\hfill Santiago, Chile}
	\vspace{0.3em}
\cvline{12.2017}{{Dark Energy from Observations.}								\hfill Punta Mita, MX}
	\vspace{0.3em}
\cvline{11.2017}{{Colloquium: Explaining the Universe with current and future probes}	\hfill Leon, MX}
	\vspace{0.3em}
\cvline{11.2017}{{Reconstructing the Universe.}									\hfill ICF-UNAM, MX}
	\vspace{0.3em}
\cvline{11.2017}{{Reconstructing the Universe.}									\hfill MCTP, MX}
	\vspace{0.3em}
\cvline{10.2017}{{Cosmology and some other stuff.}								\hfill BUAP, MX}
	\vspace{0.3em}
\cvline{08.2017}{{Scalar Field Dark Matter.}									\hfill Queretaro, MX}
	\vspace{0.3em}
\cvline{02.2017}{{A simplistic description of the current Universe.}					\hfill CINVESTAV, DF, MX}
	\vspace{0.3em}
\cvline{01.2017}{{Observational Cosmology: Constraining our Universe.}				\hfill UNAM, Morelos, MX}
	\vspace{0.3em}
\cvline{02.2016}{{The current status of the Universe.}							\hfill Science Center, NY, US}
	\vspace{0.3em}
\cvline{04.2015}{{Cosmological implications of BAO measurements: BOSS DR11.} \hfill APS, MD, US}
	\vspace{0.3em}
\cvline{}{ \textit{\small \qquad Plenary talk on behalf of the BOSS Collaboration} }
	\vspace{0.3em}
\cvline{04.2015}{{Gaussian Embedding algorithm and the BAO.} 				\hfill CMU, PA, US}
	\vspace{0.3em}
\cvline{03.2015}{{Cosmology with BAO measurements.}		 				\hfill Aspen, CO, US}
	\vspace{0.3em}
\cvline{02.2015}{{The current status of the Universe.} 						\hfill Koc University, Istanbul, TR}
	\vspace{0.3em}
\cvline{02.2015}{{The standard cosmological model: LCDM.} 					\hfill ITU, Istanbul, TR}
	\vspace{0.3em}
\cvline{01.2015}{{Gaussian Embedding algorithm and the SimpleMC code.} 			\hfill Berkeley, CA, US}
	\vspace{0.3em}
\cvline{12.2014}{{Cosmological Implications of BAO measurements.} 			\hfill SDSS Meeting, NM, US}
	\vspace{0.3em}
\cvline{}{ \textit{\small \qquad  Plenary talk on behalf of the BOSS Collaboration} }
	\vspace{0.3em}
\cvline{10.2014}{{BAO implications on Dark Energy constraints.}				\hfill  BNL, NY, US}
	\vspace{0.3em}
\cvline{08.2013}{{Model Selection applied to Dark Energy models.} 				\hfill UNAM, MX}
	\vspace{0.3em}
\cvline{09.2013}{{Dark Energy: Cosmological constant and other alternatives.} 		\hfill CINVESTAV, MX}
	\vspace{0.3em}
\cvline{04.2012}{{Comparison  of  Cosmological  Models  with  current Observations.} \hfill Cambridge, UK}{}	



%--------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\subsection{Talks}
\vspace{0.5em}
%-----------------------------------------------------------------------------------------------------------


\cvline{10.2015}{{The current status of the Universe.}						\hfill BNL, NY, US}
	\vspace{0.3em}
\cvline{06.2014}{{BAO in the Ly-$\alpha$ forest of BOSS DR11 quasars.}			\hfill BNL, NY, US}
	\vspace{0.3em}
\cvline{09.2013}{{Dark Energy: Cosmological constant and other alternatives.}		\hfill CINVESTAV, MX}
	\vspace{0.3em}
\cvline{09.2013}{{Model Selection applied to Dark Energy models.}				\hfill UNAM, MX}
	\vspace{0.3em}
\cvline{09.2013}{{Energ\'ia oscura: alternativas a la constante cosmol\'ogica.} \hfill INAOE, Puebla, MX}{}	
	\vspace{0.3em}
\cvline{02.2013}{{Constraining alternative models with future observations.}		\hfill IF, UNAM, MX}{}	
	\vspace{0.3em}
\cvline{04.2012}{{Comparison  of  Cosmological  Models  with  current Observations.} \hfill Cambridge, UK}{}	
	\vspace{0.3em}
\cvline{01.2011}{{An overview of Statistical Cosmology.}						\hfill  ININ, MX}{}	
	\vspace{0.3em}
\cvline{01.2011}{{Constraining cosmological models with current data.}			\hfill CINVESTAV, MX}{}{}
	\vspace{0.3em}
\cvline{04.2010}{{Comparing a novel closed Universe model with  CMB data.}		\hfill KICC, Cambridge, UK}{}{}	
	\vspace{0.3em}
\cvline{05.2008}{{Potential scalar field reconstruction.} 						\hfill CINVESTAV, MX}{}{}
	\vspace{0.3em}
\cvline{10.2006}{{General aspects of Dark Matter.}							\hfill CINVESTAV, MX}{}{}
	\vspace{0.3em}
\cvline{08.2005}{{Galaxy formation with Scalar Field Dark Matter.}				\hfill CCF, UNAM, MX}{}{}
	\vspace{0.3em}
\cvline{01.2005}{{What is the Universe made of: Dark Matter.}					\hfill UAEM, MX}{}{} 


%--------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\section{Hacking}
\vspace{0.5em}
%-----------------------------------------------------------------------------------------------------------

\cvline{-.2018}{PyData.													\hfill NY, US}
	\vspace{0.3em}
\cvline{08.2016}{PyData.													\hfill Chicago, IL, US}
	\vspace{0.3em}
\cvline{07.2016}{PyGotham.												\hfill UN, NY, US}
	\vspace{0.3em}
\cvline{07.2016}{Database Camp.											\hfill NY, US}
	\vspace{0.3em}
\cvline{06.2016}{8th Astronomical Data Analysis Summer School.					\hfill Chania,  GR}
	\vspace{0.3em}
\cvline{01.2015}{Symposium and Hack Week on data-intensive cosmology.			\hfill  Berkeley, CA, US}
	\vspace{0.3em}
\cvline{04.2015}{SciCoder 6 Workshop.										\hfill  NY, US}


%--------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\section{Travel grants } 
\vspace{0.5em}
%--------------------------------------------------------------------------------------------------------------------------------------------------------


\cvline{01.2018}{Cosmo Andes.											\hfill Santiago,Chile}
	\vspace{0.3em}
\cvline{12.2017}{Cosmology on the Beach.								\hfill Punta Mita, MX}
	\vspace{0.3em}
\cvline{06.2016}{Summer School in Statistics for Astronomers.					\hfill Penn State, PA, US}
	\vspace{0.3em}
\cvline{05.2016}{Statistical Challenges in 21st Century Cosmology. 				\hfill Chania, GR}
	\vspace{0.3em}
\cvline{04.2015}{American Physical Society Meeting.							\hfill MD, US}
	\vspace{0.3em}
\cvline{08.2014}{Workshop on Cosmology from Baryons at High Redshift.			\hfill  Trieste, IT}
	\vspace{0.3em}
\cvline{08.2014}{Collaboration Meeting.		 							\hfill Cambridge, UK}
	\vspace{0.3em}
\cvline{07.2014}{SDSS-III and SDSS-IV Collaboration.						\hfill	 Salt Lake City, UT, US}
	\vspace{0.3em}
\cvline{01.2014}{Essential Cosmology for the next Generation.			 		\hfill Cabo, MX}
	\vspace{0.3em}
\cvline{10.2013}{Precision Astronomy with Fully Depleted CCDs.				\hfill BNL, NY, USA}
	\vspace{0.3em}
\cvline{08.2013}{Segunda reuni\'on de estudiantes de Astronom\'ia.				\hfill INAOE, Puebla, MX}
	\vspace{0.3em}
\cvline{07.2013}{Statistical methods applied to modern cosmology. \hfill UNAM, MX}
	\vspace{0.3em}
\cvline{05.2012}{Testing General Relativity with Astrophysical Systems.			\hfill Harvard, MA, US}
	\vspace{0.3em}
\cvline{07.2011}{New Horizons for High Redshifts.							\hfill Cambridge, UK}
	\vspace{0.3em}
\cvline{07.2011}{PASCOS 2011.										\hfill Cambridge, UK}
	\vspace{0.3em}
\cvline{01.2011}{Essential Cosmology for the Next Generation.					\hfill Jalisco, MX}
	\vspace{0.3em}
\cvline{12.2010}{Fourth TRR33 Winter School.								\hfill  Passo del Tonale, IT}
	\vspace{0.3em}
\cvline{07.2008}{Summer school in Cosmology.								\hfill  ICTP, Trieste, IT}
	\vspace{0.3em}
\cvline{05.2008}{III International Meeting on Gravitation and Cosmology.			\hfill Morelia, MX}{}
	\vspace{0.3em}
\cvline{09.2007}{Latin-American School of Physics.							\hfill DF, MX}{}
	\vspace{0.3em}
\cvline{08.2007}{XXXV SLAC Summer Institute.							\hfill Stanford, CA, USA}{}
	\vspace{0.3em}
\cvline{06.2007}{International Conference on Quantum Gravity.					\hfill Morelia, MX}{}
	\vspace{0.3em}
\cvline{07.2006}{New Frontiers in Numerical Relativity.						\hfill AIE, Berlin, DE}{}
	\vspace{0.3em}
\cvline{07.2004}{XIII Summer at the National Astronomic Observatory.			\hfill Ensenada, MX}{}


%-----------------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\subsection{Domestic} 
\vspace{0.5em}
%-----------------------------------------------------------------------------------------------------------------------------------------------------------------

\cvline{08.2009}{Cluster de Alto desempeno.								\hfill UAEH, Hidalgo, MX}{}{}
	\vspace{0.3em}
\cvline{02.2008}{1er Congreso de Cosmolog\'ia.							\hfill IFUG, MX}{}{}{}
	\vspace{0.3em}
\cvline{09.2007}{2a Reuni\'on del Instituto Avanzado en Cosmolog\'ia.			\hfill CRyA-UNAM, MX}{}{}{}
	\vspace{0.3em}
\cvline{07.2007}{Advanced Summer School in Physics.						\hfill CINVESTAV, MX}{}{}{}
	\vspace{0.3em}
\cvline{04.2007}{XV Reuni\'on anual de la divisi\'on de Gravitaci\'on y F\'isica Matem\'atica.\hfill IPN, MX}{}{}{}
	\vspace{0.3em}
\cvline{01.2007}{Obreg\'on Fest.										\hfill IFUG, MX}{}{}{}	
	\vspace{0.3em}
\cvline{01.2007}{1era Reuni\'on  Instituto Avanzado de Cosmolog\'ia.				\hfill UNAM, MX}{}{}{}		
	\vspace{0.3em}
\cvline{11.2006}{VII Mexican School on Gravitation.							\hfill Playa del Carmen, MX}{}
	\vspace{0.3em}
\cvline{04.2006}{XIV Reuni\'on Anual de la Divisi\'on de Gravitaci\'on y F\'isica.		\hfill CINVESTAV, MX}{}{}{}
	\vspace{0.3em}
\cvline{07.2005}{ IV Mexican School of Astrophysics [EMA] 05.					\hfill Morelia, MX}{}{}{}
	\vspace{0.3em}
\cvline{09.2003}{3rd. Workshop Optica Moderna.							\hfill INAOE, Puebla, MX}{}{}{}
	\vspace{0.3em}
\cvline{08.2003}{XI Summer School on Physics, La visi\'on molecular de la materia.	\hfill UAEM, Morelos, MX}{}{}{}	
		\vspace{0.3em}
\cvline{08.2002}{X Summer School on Physics, La visi\'on molecular de la materia.	\hfill UAEM, Morelos, MX}{}{}{}	
%------------------------------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\section{Skills and Interests}
\vspace{0.5em}
%----------------------------------------------------------------------------------------------------------------------------------------------------------


\cvline{Programming Languages}{ \hfill Python, C/C++, Fortran, R, Bash Scripting}{}
		\vspace{0.3em}
\cvline{Maths}{\hfill Maple, Mathematica, Matlab (basic)}{}
		\vspace{0.3em}
\cvline{Op. Systems}{\hfill Linux, Windows, Mac OS X}
		\vspace{0.3em}
\cvline{Design}{\hfill Latex, HTML, CSS}
		\vspace{0.3em}
\cvline{Databases}{\hfill MySQL, SQLite}
		\vspace{0.3em}
\cvline{Useful}{\hfill Gnuplot, Git, SVN}

%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\subsection{Packages, libraries and frameworks}
\vspace{0.5em}
%----------------------------------------------------------------------------------------------------------------------------------------------------------


\cvline{Python}{\hfill Numpy, Pandas, Scipy, Scikit-learn, Beatiful Soup, Matplotlib, Bokeh, Seaborn, Flask.}
		\vspace{0.3em}
\cvline{R}{\hfill dplyr, Main ones for Stats and ML, ggplot2, Shiny}
		\vspace{0.3em}
\cvline{C/C++, Fortran}{\hfill  LAPACK, OpenMP, MPI}
		\vspace{0.3em}
\cvline{HPC Clusters}{\hfill NERSC(LBNL), Astro (BNL), Darwin (Cambridge), LaSuma-(CINVESTAV)
%\footnote{Acronyms: High Performace Computing [HPC], Application Programming Interface [API],
%Structured Query Language [SQL],  Markov chain Monte Carlo [MCMC].
}



%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\subsection{Cosmology codes}
\vspace{0.5em}
%----------------------

\cvline{}{ CAMB, CosmoMC, MultiNest, CosmoNet, CosmoSIS, SimpleMC.}
	\vspace{0.3em}
\cvline{Software Contributions}{ 
\hfill MCMC for BAO analysis for the BOSS collaboration (Python) - \href{https://github.com/ja-vazquez/SimpleMC}{\blue{SimpleMC}}\\. 
\hfill Massively parallelizable Gaussian Embedding Sampling (Python) - \href{https://github.com/ja-vazquez/GM_Sampler}{\blue{GM algorithm}}\\.
\hfill Model Independent Bayesian Reconstruction (Fortran) - \href{http://www.mrao.cam.ac.uk/facilities/software/np-camb/}{\blue{NP-CAMB}}}
\hfill Lyman-$\alpha$ analysis for the BOSS collaboration (C++) - \href{http://c3.lbl.gov:8000/Trac.Cosmology/wiki/CosmologyCodeInstallation}{\blue{Cosmology}}

%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\subsection{Non-Academic Projects}
\vspace{0.5em}
%----------------------------------------------------------------------------------------

\cvline{}{Scraping the web, Using APIs, Data manipulation with Pandas and SQL, 
	Playing with Stats and Machine Learning algorithms and Visualizations.}
	\vspace{0.3em}
\cvline{Meetups}{Regularly attending NYC meetups with keywords such as Python, R, SQL, Data science. }

\vspace{0.5em}
 \cvline{}{For further details see: 
	\href{https://github.com/ja-vazquez}{\blue {GitHub}},
	\href{https://bitbucket.org/ja_vazquez/}{\blue {Bitbucket}}.
	}

%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\subsection{Others}
\vspace{0.5em}
%----------------------------------------------------------------------------------------


\cvline{Languages}{\hfill  Spanish (Native);  English (Fluent);  German (Elementary). }{}
		\vspace{0.3em}
\cvline{ Sports}{\hfill Football (participation on national tournaments), Squash, Climbing, Jogging, Cycling.}
		\vspace{0.3em}
\cvline{}{\hfill Organiser of the national football tournament of Mexican Societies  in UK (05.2010).}
		\vspace{0.3em}
\cvline{Others}{ \hfill Reading: Economy,  Science, Science Fiction; Board games: Chess, Backgammon, Poker.}{}	
%\cvline{Extra}{Online Stocks/ETFs trader.}

\closesection{}                   % needed to renewcommands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists
%------------------------------------------------------------------------------------------------------------	
	

%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{1.0em}
\section{References}
\vspace{0.5em}
%----------------------------------------------------------------------------------------

\cventry{anze@bnl.gov}{Upton, 11973, NY, US. Tel: +1 (631) 344 8012.}
{An${ \breve{z}}$e Slosar}{Brookhaven National Lab}{}{}{}
	
\vspace{0.5em}
\cventry{mph@mrao.cam.ac.uk}{Cavendish Laboratory, CB3 0HE, UK. Tel: +44 1223 339992.}
{Mike Hobson}{University of Cambridge}{}{} 

\vspace{0.5em}
\cventry{a.n.lasenby@mrao.cam.ac.uk}{Kavli Institute for Cosmology, CB3 0HA, UK. Tel: +44 1223 337293.}
{Anthony Lasenby}{University of Cambridge}{}{} 

\vspace{0.5em}
\cventry{tmatos@fis.cinvestav.mx}{Mexico D.F, 14-740 07000, MX. Tel: +52 55 5747 3834.}
{Tonatiuh Matos}{CINVESTAV, IPN}{}{}{}{}


\vspace{4.em}
\cvline{}{\hfill Last Updated: May.2019}{}{}{}
%------------------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------------------	
%\section{Current Research}
%{The research I am currently carrying out has two main  aims: The first is to generate
%predictions of  observable quantities, within cosmological models incorporating extra
%features beyond the standard Lambda Cold Dark Matter ($\Lambda$CDM). The predictions
%are sought for the  expansion history  and the generation and evolution of perturbations.
%Secondly, advanced  Bayesian  techniques, involving the calculation of evidence and 
%nested sampling,  are carried out to  compare cosmological models using  actual data, including
%the Cosmic Microwave Background, Large-Scale  Structure and Supernovae. Future  surveys
%like  Planck and CMBPol  are also  taking  part in the analysis.}
%\vspace{0.5em}
	
%------------------------------------------------------------------------------------------------------------		
	
%\section{Personal Information}
%\cvline{Name}{Jos\'e-Alberto V\'azquez-Gonz\'alez}
%\cvline{Date of birth}{September 6, 1982} 
%\cvline{Place }{Cuernavaca, Morelos, Mexico}
%\cvline{Interests}{ BAO, CMB, Ly-$\alpha$ forest; Dark Energy, Inflation; Data analysis.} 
%\vspace{0.5em}
\end{document}

