%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[blue]{casual}           
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'

\usepackage[utf8]{inputenc}                   
\usepackage[scale=0.84]{geometry}
\AtBeginDocument{\recomputelengths}              

\usepackage{multicol}

\def\blue{\textcolor{blue}}
\def\etal{\emph{et al.~}}

\renewcommand*{\namefont}{\fontsize{25}{40}\mdseries\upshape}
\renewcommand*{\titlefont}{\fontsize{12}{40}\mdseries\upshape}

  
\firstname{Jos\'e-Alberto}
\familyname{V\'azquez}
\title{Brookhaven National Lab, U.S. Department of Energy}               
\address{Brookhaven Nat. Lab.}{Bdlg. 510-A, Upton NY. 11973} 
\phone{+1 631 344 4060} {}                   
%\fax{1223 337523}                          
\email{jv292@cam.ac.uk}                    
\email{jvazquez@bnl.gov}
\mobile{+1 631 992 0730}                    
\extrainfo{JA Vazquez} 
%\photo[74pt]{yo}                         % '64pt'
%\quote{Some quote (optional)}                
%\nopagenumbers{}                             


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

\begin{document}
\maketitle
%
%------------------------------------------------------------------------------------------------------------
\vspace{-0.7cm}
\section{Current Position}
\cventry{Oct.2013 - }{Post-doctoral Research Associate}{\hfill Brookhaven National Lab}{NY, USA}{}{}{}
\cvline{}{\emph{``Cosmological Implications of BAO measurements and Lyman-$\alpha$ forest analysis"}}{}{}{}
\cvline{}{Member of the SDSS-III/SDSS-IV collaboration. Dr.~A. Slosar}
\vspace{0.3em}
%An${ \breve{z}}$e
%{The application of the BAO technique to large cosmological surveys has enabled the first 
%percent-level measurements of absolute distances beyond the Milky Way. In combination with 
%CMB and SN data, these measurements yield impressively tight constraints on the 
%cosmic expansion history and correspondingly stringent tests of dark energy theories. 
%Over the next year, the strength of these tests will advance significantly with the final 
%results from BOSS and the CMB polarization and improved temperature maps from Planck. 
%In the longer term, BAO measurements will gain in precision and redshift range through 
%a multitude of ongoing or planned spectroscopic surveys, including SDSS-IV eBOSS, 
%HETDEX, DESI, WEAVE, Euclid, and WFIRST.}\\

\cvline{Interests}{ BAO, CMB, Ly-$\alpha$ forest; Dark Energy, Inflation; Data analysis.} 
\cvline{} {\href{http://www.cosmo.bnl.gov/www/jvazquez/}{\blue{\underline{Website}}}, 
		\href{https://www.linkedin.com/in/jalbertovazquez}{\blue{\underline{LinkedIn}}}, 
		\href{https://github.com/ja-vazquez}{\blue{\underline{GitHub}}} }
%---------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{0.0em}





\section{Publications}
\cvline{*}{For further details and citations: 
	\href{http://scholar.google.com/citations?user=PCuxBOkAAAAJ&hl=en}{\blue {\underline{Google Scholar}}}, 
	\href{http://inspirehep.net/author/profile/J.A.Vazquez.1}{ \blue{\underline{Inspire}}},
	\href{https://www.researchgate.net/profile/J_Vazquez3}{ \blue{\underline{Research gate}}}}
	
\cvline{[1]}{Michael Blomqvist \etal  \emph{Broadband distortion modeling in Lyman-$\alpha$ forest BAO fitting.}} 
\cvline{}{Submitted to JCAP. \href{http://arxiv.org/abs/1504.06656}{ \hfill \blue{\underline{arXiv:1504.06656}}}}
	
\cvline{[2]}{Rupert A.C. Croft \etal \emph{Large-scale clustering of Lyman-alpha emission intensity from SDSS/BOSS.}
	{Submitted to MNRAS. \href{http://arxiv.org/abs/1504.04088}{\hfill \blue{\underline{arXiv:1504.04088}}}} }
	
\cvline{[3]}{Ozgur Akarsu, Tekin Dereli, JAV. \emph{A divergence-free parametrization for dynamical dark energy.}
	{JCAP, 1506 (2015) 06, 049. \href{http://arxiv.org/abs/1501.07598}{\hfill \blue{\underline{arXiv:1501.07598}}}}}

\cvline{[4]}{Shadab Alam \etal \emph{The Eleventh and Twelfth Data Releases of the Sloan Digital Sky Survey: 
	Final Data from SDSS-III.} {ApJs} 219 (2015) 1, 12. \href{http://arxiv.org/abs/1501.00963}
	{\hfill \blue{\underline{arXiv:1501.00963}}}}
		
\cvline{[5]}{ JAV, Mariana Carrillo, Gabriel German, Alfredo Herrera, J.C. Hidalgo. 
	\emph{Constraining Hybrid Natural Inflation with recent CMB data.} {JCAP} 1502 (2015) 02, 039.
	 \href{http://arxiv.org/abs/arXiv:1411.6616}{\hfill \blue {\underline{arXiv:1411.6616}}}}
		
\cvline{[6]}{\'Eric Aubourg \etal \emph{Cosmological Implications of baryon acoustic oscillation (BAO) measurements.}
 	Accepted to {PRD}.  \href{http://arxiv.org/abs/arXiv:1411.1074}{\hfill \blue {\underline{arXiv:1411.1074}}}}		

\cvline{[7]}{JAV \etal \emph{Reciprocity invariance 
	of the Friedmann equation, missing matter and double dark energy.} Submitted to  
	{PRD.} \href{http://arxiv.org/abs/1208.2542}{\hfill \blue {\underline{arXiv:1208.2542}}}} 
	
\cvline{[8]}{JAV, M. Bridges, Yin-Zhe Ma, M.P. Hobson. \emph{Constraints on the Tensor-to-Scalar 
	ratio for non-power law models.}  
	{JCAP} 08(001) 2013, \href{http://arxiv.org/abs/1303.4014}{\hfill \blue {\underline{arXiv:1303.4014}}}} 
	
\cvline{[9]}{JAV, M.P. Hobson, M. Bridges, A.N. Lasenby. \emph{Reconstruction of the Dark Energy equation of  state.}
	JCAP, 09(020), 2012. \href{http://arxiv.org/abs/1205.0847}{\hfill \blue{\underline{arXiv:1205.0847}}}}

\cvline{[10]}{JAV, M.P. Hobson, M. Bridges, A.N. Lasenby. \emph{Model selection applied to 
	reconstruction of the Primordial Power Spectrum.} 
	{JCAP} 006(106), 2012. \href{http://arxiv.org/abs/1203.1252}{\hfill \blue{\underline{arXiv:1203.1252}}}}

\cvline{[11]}{JAV, A.N. Lasenby, M.P. Hobson, M. Bridges. \emph{A Bayesian study of the 
	primordial power spectrum from a novel closed universe.}
	{MNRAS} 422, 1948-1956, 2011. \href{http://arxiv.org/abs/1103.4619}{\hfill \blue{\underline{arXiv:1103.4619}}}}

\cvline{[12]}{Tonatiuh Matos, Jos\'e-Rub\'en Lu\'evano, Israel Quiros, L. Arturo Urena-L\'opez,  JAV.
	\emph{Dynamics of scalar field dark matter with a cosh potential.}
	{PRD} 80, 123521, 2009. \href{http://arxiv.org/abs/0906.0396}{\hfill \blue{\underline{arXiv:0906.0396}}}}

\cvline{[13]}{Tam\'e Gonz\'alez, Tonatiuh Matos, Israel Quiros, JAV. \emph{Self-interacting 
	Scalar Field Trapped in a Randall-Sundrum Braneworld.}
	{PLB} 676, 161-167, 2009. \href{http://arxiv.org/abs/0812.1734}{\hfill \blue{\underline{arXiv:0812.1734}}}} 

\cvline{[14]}{Tonatiuh Matos, JAV, Juan Magana. \emph{$\phi^2$ as Dark Matter.}
	{MNRAS} 393, 1359-1369, 2008.}{}{\href{http://arxiv.org/abs/0806.0683}{\hfill \blue{\underline{arXiv:0806.0683}} }}

\cvline{[15]}{Tonatiuh Matos, Jos\'e-Rub\'en Luevano, Hugo Grac\'ia Compe\'an, JAV. 
	\emph{An alternative Interpretation for the Moduli Fields of the Cosmology Associated to Type IIB Supergravity with Fluxes.}
	{IJMPA}  23, 1949-1962, 2008. \href{http://arxiv.org/abs/hep-th/0511098}{\hfill \blue{\underline{arXiv:0511098}}}}

%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{0.5em}


\subsection{In Preparation \href{http://www.cosmo.bnl.gov/www/jvazquez/files/Research.html}{\small{\blue{\underline{(link)}}}}}

\cvline{[1p]}{BOSS Collaboration. \emph{The clustering of galaxies in the SDSS-III Baryon Oscillation
	Spectroscopic Survey: Baryon Acoustic Oscillations in the Data Release 12 Galaxy Sample.}}
		
\cvline{[2p]}{JAV, An${ \breve{z}}$e Slosar, Hee-Jong Seo, David Weinberg. 
	\emph{Early Dark Energy: Reality and Fiction.} 
	\href{https://github.com/ja-vazquez/Early_DE}{\hfill \blue{\underline{Link}}}} 

\cvline{[3p]}{JAV, An${ \breve{z}}$e Slosar, Andreu Font-Ribera, Patrick McDonald. 
	\emph{Gaussian Embedding -- massively parallelizable sampling algorithm.}
	\href{https://github.com/ja-vazquez/GM_Sampler}{\hfill \blue{\underline{Link}}}}

\cvline{[4p]}{Sukhdeep Singh, Rachel Mandelbaum, An${ \breve{z}}$e Slosar, JAV.
	\emph{Cosmological constraints from galaxy-galaxy lensing and galaxy clustering.}
	\href{https://github.com/ja-vazquez/Upsilon}{\hfill \blue{\underline{Link}}}}
	
\cvline{[5p]}{Gabriel German, Graham Ross, JAV. \emph{Observable bounds in Hybrid Natural 
	Inflation from sub-Planckian field excursion.} }
	
\cvline{[6p]}{JAV, M.P. Hobson, A.N. Lasenby, M. Bridges. \emph{Cosmological constraints on Modified Gravity.}
	\href{http://www.cosmo.bnl.gov/www/jvazquez/files/Research.html}{\hfill \blue{\underline{Link}}}}

\cvline{[7p]}{Ozgur Akarsu, Tekin Dereli, Suresh Kumar, JAV.  
	\emph{Cosine-law for deceleration parameter.}}
	
\cvline{[8p]}{S. Hee, JAV, W. Handley, A.N. Lasenby, M.P. Hobson. \emph{Analysis of Data Variations from a 
	Constant Dark Energy Equation of State.}}	
%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{0.5em}


\subsection{Reviews}
\cvline{[1R]}{JAV, Tonatiuh Matos. \emph{Dark matter in the Universe: goals and challenges.
	{Rev. Mex. de F\'isica E}. 54, 193-202, 2008. \href{http://www.scielo.org.mx/scielo.php?pid=S1870-35422008000200012&script=sci_abstract} {\hfill \blue{\underline{RMF, 1870-3542}}}}}
%	
\cvline{[2R]}{JAV, Tonatiuh Matos. \emph{Constraining Cosmological Inflation.}
	 Accepted for publication by {Rev. Mex. Fis. E.}}
%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{0.5em}


\subsection{Conference Proceedings}
\cvline{[1C]}{Tonatiuh Matos, JAV, Juan Magana. \emph{Study of Several Potentials 
	as Scalar Field Dark Matter Candidates.}
	{AIP Conf. Proc.} 1083, 144-170, 2008. \href{http://inspirehep.net/record/808386} {\hfill \blue{\underline{AIP, 808386}}}}

\cvline{[2C]}{Tonatiuh Matos, Jos\'e Rub\'en Luevano, L. Arturo Urena, JAV. \emph{Alternative 
	interpretation for the moduli fields of string theories.} 
	{J. Phys. Conf. Ser.} 91, 012014, 2007. \href{http://inspirehep.net/record/773227} {\hfill \blue{\underline{JP, 773227}}}}
%----------------------------------------------------------------------------------------------------------------------------------------------------------
\vspace{0.0em}

%------------------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------------------	
%\section{Current Research}
%{The research I am currently carrying out has two main  aims: The first is to generate
%predictions of  observable quantities, within cosmological models incorporating extra
%features beyond the standard Lambda Cold Dark Matter ($\Lambda$CDM). The predictions
%are sought for the  expansion history  and the generation and evolution of perturbations.
%Secondly, advanced  Bayesian  techniques, involving the calculation of evidence and 
%nested sampling,  are carried out to  compare cosmological models using  actual data, including
%the Cosmic Microwave Background, Large-Scale  Structure and Supernovae. Future  surveys
%like  Planck and CMBPol  are also  taking  part in the analysis.}
%\vspace{0.5em}
	
%------------------------------------------------------------------------------------------------------------		
	
%\section{Personal Information}
%\cvline{Name}{Jos\'e-Alberto V\'azquez-Gonz\'alez}
%\cvline{Date of birth}{September 6, 1982} 
%\cvline{Place }{Cuernavaca, Morelos, Mexico}
%\cvline{Interests}{ BAO, CMB, Ly-$\alpha$ forest; Dark Energy, Inflation; Data analysis.} 
%\vspace{0.5em}
\end{document}

